State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-22 prism-backend/research/soa_review/ac.tex
Added note on Nym Credentials.

@@

>>>>

\item[\cite{halp20}:] Builds on Coconut credentials and a blockchain -- in theory,
  any blockchain with smart-contract capability, although it seems they are building
  their own blockchain. This paper is in the frontier of academic and industry
  work. On the cryptographic side, the credentials they build are essentially an
  extension of Coconut credentials (although the extension is not described, nor
  formalized). Users can combine multiple Coconut credentials into one Nym
  Credential. In order to control Sybil attacks, Nym Credentials are obtained
  in exchange of Nym Tokens (how users get hold of these, is not described).
  Service Providers receive Nym Tokens in exchange of offering their services
  through the network.

@@

\item[\cite{halp20}:] No formal definition is given. The following properties
  are claimed: undetectability (this seems similar to traceability in group sigs),
  unlinkability, selective attributes disclosure, unforgeability, persistent
  accounts, sybil resistance, extensibility, availability, decentralization.
